### 2016-10-08 text/MS.Rmd
attempt 1 to restructure code using remake

```{r, results="hide", warnings=FALSE, echo=FALSE, message=FALSE}
load('../output/RDatafiles/analyses.RData')
load('../output/RDatafiles/numbers.RData')
source('../R/functions-analyses.R')
source('../R/functions-figures.R')
cleanbib()
myRefs   <-  listBibs()
exporBibs(myRefs, erase=TRUE)
```
**Temperature effects on mass-scaling exponents in colonial animals: a manipulative test**

@@

>>>>

```{r, results="hide", warnings=FALSE, echo=FALSE, message=FALSE}
cleanbib()
myRefs   <-  listBibs()
exporBibs(myRefs, erase=TRUE)
```
**Temperature effects on mass-scaling exponents in colonial animals: a manipulative test**

@@

```{r}
ci95Estimates     <-  numbersList$ci95Estimates
metabolicDiff     <-  numbersList$metabolicDiff
averageEstimates  <-  numbersList$averageEstimates
q10andErs         <-  numbersList$q10andErs
tempDeltas        <-  numbersList$tempDeltas
```
